%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                       NOTES                                                                       %
% Aohd and Jason is sitting on Jason's porch smoking a joint and sees mothman flying over head.                                                     %
% Aohd looks at Jason and says, "Do we have any bridges here?" Jason replies, "Yeah there's one that crosses the river right before you get in town"%
% Aohd replies, "Not anymore"                                                                                                                       %
%                                                                                                                                                   %
% And that will lead to a chain of events that will make Jason realize Aohd's real                                                                  %
%                                                                                                                                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{memoir}[12px]
\usepackage{hyperref}
\usepackage{memhfixc}
\usepackage{indentfirst}
\pagenumbering{gobble}
\begin{document}
\being{titlepage}
\title{Aohd meets Mothman}
\author{joshp1}
\date{}
\end{titlepage}
\maketitle
\chapter {Aohd meets Mothman}
Jason and Aohd are sitting on Jason's porch. Passing a joint back and forth. Jason laughs and says, "Man this is some good shit" Aohd shrugs and says, "I've had better" Jason laughs laying back saying, "I'm sure you have. I've had some of that good shit to" \\

They sit on the porch eating. After a bit Jason blinks and says, "What the hell is that". Aohd shrugs starring off into space thinking. Jason shakes his head and says, "Is that mothman?" Aohd looks up and says, "Do we have any bridges near by?" Jason points to his right and says, "Yeah. Right before you get into town" Aohd nods and says, "Not anymore"\\

Jason laughs but right then ambulances and police cars zoom past with their sirens going. A second later they hear a fire truck horn and three latter trucks goes by. Jason blinks and goes inside.\\

Jason comes out shocked and says, "The Gold bridge just fell" Aohd nods and says, "Damn, wish we had something to eat" Jason points and says, "People just got killed and your worried about the munches?" Aohd nods and says, "Chili dogs would be good" \\

Just then a donkey pushing a hotdog stand walks by. Aohd perks up and fly's down to it. Jason is amazed and sits down. When the man stops and makes Aohd two chili and cheese dogs then Aohd puts up his wing and the man makes another. He bags them and Aohd picks them up and fly's off. Leaving the man mad yelling, "Hey asshole you got to pay for that!" He then flips him off and says, "Fucking wierd birds" Jason is cracking up when Aohd lands back on his porch and says, "Your hilarious man", forgetting about the bridge. Aohd hands him a chili dog and says, "Here I got you one" Jason is baffled and says, "Woah this is some good shit" Aohd nods and says, "One second" He pics up a couple rolls of quarters and fly's back other to the vender.\\


\end {document}