%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                       NOTES                                                                       %
% Aohd and Jason is sitting on Jason's porch smoking a joint and sees mothman flying over head.                                                     %
% Aohd looks at Jason and says, "Do we have any bridges here?" Jason replies, "Yeah there's one that crosses the river right before you get in town"%
% Aohd replies, "Not anymore"                                                                                                                       %
%                                                                                                                                                   %
% And that will lead to a chain of events that will make Jason realize Aohd's real                                                                  %
%                                                                                                                                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{memoir}[12px]
\usepackage{hyperref}
\usepackage{memhfixc}
\usepackage{indentfirst}
\begin {document}
\chapter* {Aohd meets Mothman}
Jason and Aohd are sitting on Jason's porch, passing a joint back and forth. Jason laughs and says, "Man this is some good shit" Aohd shrugs and says, "I've had better" Jason laughs laying back saying, "I'm sure you have. I've had some of that good shit to" \\

They sit on the porch eating. After a bit Jason blinks and says, "What the hell is that". Aohd shrugs starring off into space thinking. Jason shakes his head and says, "Is that mothman?" Aohd looks up and says, "Do we have any bridges near by?" Jason points to his right and says, "Yeah. Right before you get into town" Aohd nods and says, "Not anymore"\\

Jason laughs but right then ambulances and police cars zoom past with their sirens going. A second later they hear a fire truck horn and three latter trucks goes by. Jason blinks and goes inside.\\

Jason comes out shocked and says, "The Gold bridge just fell" Aohd nods and says, "Damn, wish we had something to eat" Jason points and says, "People just got killed and your worried about the munches?" Aohd nods and says, "Chili dogs would be good" \\

Just then a donkey pushing a hotdog stand walks by. Aohd perks up and fly's down to it. Jason is amazed and sits down. When the man stops and makes Aohd two chili and cheese dogs then Aohd puts up his wing and the man makes another. He bags them and Aohd picks them up and fly's off. Leaving the man mad yelling, "Hey asshole you got to pay for that!" He then flips him off and says, "Fucking wierd birds" Jason is cracking up when Aohd lands back on his porch and says, "Your hilarious man", forgetting about the bridge. Aohd hands him a chili dog and says, "Here I got you one" Jason is baffled and says, "Woah this is some good shit" Aohd nods and says, "One second" He pics up a couple rolls of quarters and fly's back other to the vender.\\

Jason is on his porch blinking amazed, when Aohd returns Jason asks, "Aohd, how did you pick those up?" Aohd, shrugs and says, "With my wing" Jason blinks and says, "It makes since now" Aohd even more confused says, "What does?" Jason mesmerized says, "Your real. This whole time I thought I was so blazed I was hallucinating" Aohd laughs and says, "Well how do you explain that roll of money?" Jason replies, "I thought I had put my pay check's money in the wrong pocket" Aohd laughs and says, "Explain the chili dogs" Jason replies, "I had no idea I thought I blacked out or was so blazed I forgot buying them. Donny the guy you bought this from walks by here about five times a day anyway" 

Aohd sits down then suddenly Jason's eyes get big and says, "Holy shit, you're a fucking phoenix" Aohd nods and says, "Yep, last time I checked" Jason looking around says, "That was fucking mothman" He stands up and starts passing, "You guys are myths what's next bigfoot is going to show up?" He then says, "OH fuck. There he is" He then faints. 

Jim a black bear walks up panicked and says, "Is he ok?" Aohd shrugs and says, "Guess he needed a nap" Jim is in disbelief and says, "That man needs help" As he runs up on the porch. Aohd looks and says, "He's breathing" Jim crotches down beside Jason who's starting to wake. 

When he opens his eyes he sees the bear checking his pulse and yells, "Hey!" Jim calmly says, "You fainted I was just checking your pulse. Your friend there that strange looking chicken didn't even bother" Aohd looks down and says, "Hey, I'm not a chicken" Jim looks back with a angry look but don't say anything. He just looks back at Jason and says, "If you feel faint or anything else like that get to the hospital" Jason agrees and Jim goes on his way but first giving Aohd a pissed look.

Jason shakes his head and says, "So your a fucking phoenix and that was mothman, and that down the street is bigfoot". Aohd looks down the street and sees a large bush with two branch going out on the sides. Aohd says, "The bigfoot I think is a hallucination but yeah that was mothman and I'm a phoenix" He says phoenix with a bit of pride. 

Jason stands up and says, "Damn, sorry dude for thinking you where made up" Aohd shrugs and says, "No problem" He then looks back and says, "Hey you thought I was fake?"
\end {document}